The Revisited Hidden Weight Bit Function

### 2025-08-29 paper.tex
M

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{microtype}

\newcommand{\AI}{\mathsf{AI}}
\newcommand{\Bfn}[1]{\mathcal{B}_{#1}}
\newcommand{\BN}{\mathcal{B}_n}
\newcommand{\C}{\mathbb{C}}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\degg}{\mathsf{deg}}
\newcommand{\dis}{\mathsf{c_1}}
\newcommand{\Dkna}[3]{\mathsf{D}_{#2,#1}(a)}
\newcommand{\Dtkna}[4]{\mathsf{D}_{#1,#2,#3}(#4)}
\newcommand{\ee}{\mathrm e\mkern1mu}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\Ekn}[2]{\mathsf{E}_{#1,#2}}
\newcommand{\etal}{\textsl{et al.}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\FAI}{\mathsf{FAI}}
\newcommand{\hd}{\mathsf{d_H}}
\newcommand{\hwbf}{\textsf{HWBF}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\ii}{\mathrm i\mkern1mu}
\newcommand{\kraw}[3]{\mathsf{K}_{#1}(#2,#3)}
\newcommand{\myurl}[1]{\footnote{\texttt{\url{#1}}}}
\newcommand{\NL}{\mathsf{NL}}
\newcommand{\phikn}[2]{\varphi_{#1,#2}}
\newcommand{\w}{\mathsf{w_H}}
\newcommand{\WD}[2]{\mathcal{WD}^{#1}_{#2}}
\newcommand{\wt}[1]{\mathcal W_{#1}} 
\newcommand{\wtk}[2]{\mathcal{W}_{#1,#2}}
\newcommand{\Z}{\mathbb{Z}}

@@

    \begin{proof}
    	We use the expressions from Table~\ref{tab:Dkna_small_k}, and replace $p$, $q$ and $r$ by their respective values. For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$, respectively, in the expression $\Dkna n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dkna n2a=0$. This checking can be automatized by a computer algebra system, for which we provide a \textsf{SageMath} implementation.\myurl{https://github.com/se-tim/Revisited-HWBF.git}
    \end{proof}

@@

    In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the bound $B_n$ obtained through the above method and to the bound from Corollary~\ref{cor:bound_walsh_cauchy}. Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n\in[1,80]$. The method described above offers a tighter bound compared to Corollary~\ref{cor:bound_walsh_cauchy}. Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$. We provide a \textsf{SageMath} implementation to obtain the bound $B_n$.\myurl{https://github.com/se-tim/Revisited-HWBF.git}

@@

        \subsubsection{\discintname}
        The authors have no competing interests to declare
        that are relevant to the content of this article.
    \end{credits}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}

\newcommand{\AI}{\mathsf{AI}}
\newcommand{\Bfn}[1]{\mathcal{B}_{#1}}
\newcommand{\BN}{\mathcal{B}_n}
\newcommand{\C}{\mathbb{C}}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\degg}{\mathsf{deg}}
\newcommand{\dis}{\mathsf{c_1}}
\newcommand{\Dkna}[3]{\mathsf{D}_{#2,#1}(a)}
\newcommand{\Dtkna}[4]{\mathsf{D}_{#1,#2,#3}(#4)}
\newcommand{\ee}{\mathrm e\mkern1mu}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\Ekn}[2]{\mathsf{E}_{#1,#2}}
\newcommand{\etal}{\textsl{et al.}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\FAI}{\mathsf{FAI}}
\newcommand{\hd}{\mathsf{d_H}}
\newcommand{\hwbf}{\textsf{HWBF}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\ii}{\mathrm i\mkern1mu}
\newcommand{\kraw}[3]{\mathsf{K}_{#1}(#2,#3)}
\newcommand{\NL}{\mathsf{NL}}
\newcommand{\phikn}[2]{\varphi_{#1,#2}}
\newcommand{\w}{\mathsf{w_H}}
\newcommand{\WD}[2]{\mathcal{WD}^{#1}_{#2}}
\newcommand{\wt}[1]{\mathcal W_{#1}} 
\newcommand{\wtk}[2]{\mathcal{W}_{#1,#2}}
\newcommand{\Z}{\mathbb{Z}}

@@

    \begin{proof}
    	We use the expressions from Table~\ref{tab:Dkna_small_k}, and replace $p$, $q$ and $r$ by their respective values. For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$, respectively, in the expression $\Dkna n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dkna n2a=0$. This checking can be automatized by a computer algebra system, for which we provide a \textsf{SageMath} implementation.\footnote{\url{https://github.com/se-tim/Revisited-HWBF.git}}
    \end{proof}

@@

    In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the bound $B_n$ obtained through the above method and to the bound from Corollary~\ref{cor:bound_walsh_cauchy}. Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n\in[1,80]$. The method described above offers a tighter bound compared to Corollary~\ref{cor:bound_walsh_cauchy}. Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$. We provide a \textsf{SageMath} implementation to obtain the bound $B_n$.\footnote{\url{https://github.com/se-tim/Revisited-HWBF.git}}

@@

        \subsubsection{\discintname}

        The authors have no competing interests to declare that are relevant to the content of this article.
    \end{credits}
